Regular singular Volterra equations on complex domains

### 2023-08-31 reg-sing-volterra.tex
Update condition diag0 in section 4.3 Notation

\item Work on acknowledgements

@@

\item \textbf{(Aaron)} Add people Aaron had conversations with
\item \textbf{(Aaron)} Think about rephrasing FMHJ acknowledgement (ERC one can't be changed).

@@

In addition, for each $\sigma > \tau$, the bound
\[ \big|\hardker(a, a')\big| < \frac{\sigma}{\zeta(a)} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
\end{conditions}
For most of our results, we'll need to make sure that $\domain$ doesn't touch any singularities of $\hardpart$ other than the one at $\zeta = 0$. We'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal. These requirements can be combined into one condition.
\begin{conditions}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} For some constant $\lambda_\Delta$, we have
\[ \big| \hardker(a, a') \big| \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a, a' \in \domain$.
\end{conditions}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.

@@

Our conditions on Volterra operators change to describe a regular singularity at $\zeta = \alpha$. For example, consider a Volterra operator $\hardpart^\alpha$ of the kind described in Section~\ref{setting:basic}, with kernel $\hardker^\alpha$. This operator now satisfies Condition~\eqref{cond:sing} if for some real, positive constant $\tau_\alpha$, the difference
\[ \hardker^\alpha(a, a) - \frac{\tau_\alpha}{\zeta(a) - \alpha} \]
is bounded on a neighborhood of $\zeta(a) = \alpha$ in $\domain_\alpha$, and for each $\sigma > \tau_\alpha$, the bound
\[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. \textcolor{Tomato}{[Also describe change for Condition~\eqref{cond:diag-basic}.]} Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
\[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain_\alpha$.
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula
\begin{equation}\label{laplace:int} 
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
It's a function on the frequency domain because it depends on the frequency variable $z$.
\subsubsection{Action on integral operators}\label{sec:L-int-op}
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{-\nu}{\zeta}{\alpha}\,\fracderiv{-\mu}{\zeta}{\alpha} & = \fracderiv{-\nu-\mu}{\zeta}{\alpha} & \nu, \mu \in (0, \infty),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.

>>>>

\item \textcolor{gray}{Work on acknowledgements}

@@

\item \textcolor{gray}{\textbf{(Aaron)} Add people Aaron had conversations with}
\item \textcolor{gray}{\textbf{(Aaron)} Think about rephrasing FMHJ acknowledgement (ERC one can't be changed).}

@@

In addition, for each $\sigma > \tau$, the bound
\[ \big|\hardker(a, a')\big| < \frac{\sigma}{\zeta(a)} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. \textcolor{orange}{[shouldn't be $|\zeta(a)|$ in the denominator?]}
\end{conditions}
For most of our results, we'll need to make sure that $\domain$ doesn't touch any singularities of $\hardpart$ other than the one at $\zeta = 0$. We'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal. These requirements can be combined into one condition.
\begin{conditions}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} For some constant $\lambda_\Delta$, we have
\[ \big| \hardker(a, a') \big| \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a, a' \in \domain$.
\end{conditions}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.

@@

Our conditions on Volterra operators change to describe a regular singularity at $\zeta = \alpha$. For example, consider a Volterra operator $\hardpart^\alpha$ of the kind described in Section~\ref{setting:basic}, with kernel $\hardker^\alpha$. This operator now satisfies Condition~\eqref{cond:sing} if for some real, positive constant $\tau_\alpha$, the difference
\[ \hardker^\alpha(a, a) - \frac{\tau_\alpha}{\zeta(a) - \alpha} \]
is bounded on a neighborhood of $\zeta(a) = \alpha$ in $\domain_\alpha$, and for each $\sigma > \tau_\alpha$, the bound
\[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.  
In addition, $\hardker^\alpha$ satisfies Condition~\eqref{cond:diag-basic} if for some constant $\lambda_\Delta$
\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{|\zeta(a)-\zeta(a')|}\]
over all $a,a'\in\domain_\alpha$. 
Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
\[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain_\alpha$.
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula
\begin{equation}\label{laplace:int} 
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
It's a function on the frequency domain because it depends on the frequency variable $z$.
\subsubsection{Action on integral operators}\label{sec:L-int-op}
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{-\nu}{\zeta}{\alpha}\,\fracderiv{-\mu}{\zeta}{\alpha} & = \fracderiv{-\nu-\mu}{\zeta}{\alpha} & \nu, \mu \in (0, \infty),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.
